\begin{acknowledge}
It is difficult to over state how much I have learned during my seven years in graduate school.
Not only pertaining to physics, engineering, and computer science but about myself, my friends, and my communities.
In all of my endeavors, I was met and shaped by a countless number of people who each, in their own way, have challenged, encouraged, and taught me.
For this, I am tremendously grateful.

Thank you most of all to my adviser, Thomas Killian.
Tom, I have an immense respect for your unwavering standards and requirement of the best from those under your tutelage.
You have emboldened me for many years to explore and expand my capabilities and I sincerely hope that I may one day motivate others as you have motivated me.
Thank you to Professors Randy Hulet, Barry Dunning, and Kaden Hazzard.
My conversations and classes with each of you have always led me to a deeper appreciation and more complete understanding of atomic physics.
Thank you to all of my lab mates in the Killian lab.
I look forward to learning about each of your successes and triumphs in the coming years.
In particular, thank you to Joe Whalen, Roger Ding, and Thomas Langin for the many long hours spent discussing physics and the always ready willingness to debate ideas.
Thank you to Brian DeSalvo for his infinite patience and inspirational work ethic.
I truly admire you Brian and wish you all the success, joy, and happiness that life can bring.
Thank you to Francisco Camargo, for the rigor and resolve with which you tackle problems.
Your friendship has been invaluable and a lesson in not taking one's self too seriously.

Thank you to Jesse Choe, Katie Dessi, Arpan Bhowmik, and once more Francisco for the nights spent dog-fighting in space and arguing over who is Merlin.
Your solidarity came at a much needed time and I will always hold those tournaments and memories dear to my heart.
Thank you to my fellow Spuds, Allison and Eric.
You both are incredible community builders and leaders.
I wish both of you the greatest prosperity.
Thank you to Nikki, Kenny, Maven, Nirry, Mongbat, Puck, and Bottles. 
You all bring a brightness to this world that is much needed. 
I greatly appreciate each of you and your friendship has meant the world.
Thank you to Michelle Crane and all of the teachers throughout the years that have pushed me to improve and provided guidance when it was needed most.

Thank you to all of my family, without whom I would surely have never appreciated why ``can't never did nothing".
Thank you specifically to my mothers, Jennifer Born and JoAnne Ethington.
Jennifer, you have always been a bastion of strength and resolve, qualities which I greatly admire and hope to embody as I make my way in the world.
To Jim and Sandy Ethington, thank you for instilling in me a sense of adventure and a love of making things.
Thank you to my grandmother, Rosemary Aman. 
Mamere, you have always been there for me with an abundance of compassion, support, and generosity. 
I could not have accomplished this feat without you!
Finally, thank you to my Topl co-founders, Christopher Georgen and Kim Raath, for all of their personal encouragement and prodigious dedication to creating a lasting impact on the world.
To all of my Topl family, I am forever indebted to every one of you for the purposeful zeal each of you brings to building this company with us!
I am so incredibly excited to dedicate myself to undertake this formidable dream with you all.
Lastly, thank you to my dog Bec.
His stoicism and gentleness have been an immense comfort throughout the most tumultuous of times.

\end{acknowledge}