\chapter{Progress towards studies of quantum magnetism}
\label{ch:chap6}

A straightforward extension of the work presneted in this thesis would be to control interparticle spacing via an optical lattice. For these and additional experiments using quantum degenerate fermionic strontium we purchased and installed an optical lattice system. Our lattice is implemented using a Coherent Verdi V-18 which is shapped and propagated to our science chamber in free space. \hl{Fig} shows the optical path for each arm of our cubic lattice. 

Unfortunately, complications due to heating when loading the lattice has limited our success in this optical trap. I want to go over what we have been able to do so far with the lattice.

How did we characterize?
	Kaptiza-dirac extension
	
What convinced us we were having problems?

What are some ideas we could do in the lattice?
	Zeno
	faster cooling via stimulated raman potentailly? (can I model this somehow?)
	repulzively bound molecules?
	use interaction control in lattice with the zeno thing
	
	

\section{Optical lattice: installation and characterization}
\label{sec:lattice}

\subsection{Background}
\label{ssec:lattice_background}

\subsection{Setup}
\label{ssec:lattice_setup}

\subsection{Measurement and results}
\label{ssec:lattice_tests}

\section{Spin manipulation of $^{87}$Sr}
\label{sec:spin_pol}

Here is where I need to introduce and characterize the \hl{LCR}

Averaging images together (how to use this code specifcally)

\section{Search for narrowline PA molecules using various spin mixtures}
\label{sec:87PAS}